### 2017-04-03 paper/modes.tex
pass on section2

Notice that an important aspect in deciding which configuration to use
(or in designing new test suites) is the possibility of race
conditions on shared data during execution. For instance,
configuration \ParClassSeqMeth{} may be preferable over
\SeqClassParMeth{} when it is clear that several test methods in one
class perform operations involving one given variable that is visible
statically or within the scope of the test class.

Considering efficiency, the configuration \SeqClassParMeth{} may
speedup the execution of test classes composed of small test methods
involving variables that is visible within the scope of the method.
Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several test classes with few test methods.
Finally, the configuration \ParClassParMeth{} does not impose any 
sequential execution but it is more likely to manifest data-races as 
methods from different classes run in parallel.

@@

The list below shows the choices to control parallelism through the
build system, \eg{}, Maven.  The build system can spaw multiple JVMs,
each running on its own OS process on a given CPU and handling a
partition of the test set.

@@

Several build systems support the execution of test classes in forked
processes running a JVM. In the configuration \ForkSeq{}, each spawned
process runs a different test class at time and the builder merges the
results from each execution. In the configuration \ForkParMeth{}, the
build system forwards settings to the underlying testing framework to
enable parallel execution within each process in addition to running
test classes on different processes.  However, some configurations
(\eg, \ParClassSeqMeth) may not take effect since only one test class
can run in a forked process at time.  To the best of our knowledge, we
are unaware of any build system capable of running multiple classes at
time within a forked process.

@@

%%  LocalWords:  parallelization CPUs JUnit TestNG NUnit multi JVM de
%%  LocalWords:  JVMs falar explicar configuracao ilustrada levanta
%%  LocalWords:  uma por cria cada executar paralelo escapeinside

>>>>

Notice that an important aspect in deciding which configuration to use
(or in designing new test suites) is the possibility of race
conditions on shared data during execution.  Data sharing can occur
through state that is reachable from statically-declared variables in
the program or through variables declared within the scope of the test
class~\cite{luo-etal-fse2014}.  Considering data race avoidance,
intuitively, configuration \SeqClassParMeth{} is preferable over
\ParClassSeqMeth{} when it is clear that test methods in a class do
not manipulate shared state, which can be challenging to
determine~\cite{bell-etal-esecfse2015}, whereas \ParClassSeqMeth{} is
preferable over \SeqClassParMeth{} when it is clear that several test
methods in one class perform operations involving shared data.
Configuration \ParClassParMeth{} is more likely to manifest data races
during execution as it does not restrict scheduling orderings. Note
that speedups depend on several factors, including the test suite size
and distribution of test methods per class.

@@

The list below shows the choices to control parallelism through the
build system, \eg{}, Maven.  The build system can spawn multiple JVMs,
each running on its own OS process on a given CPU and handling a
partition of the test set.

@@

%% In the configuration \ForkSeq{}, each spawned
%% process runs a different test class at time and the builder merges the
%% results from each execution. In the configuration \ForkParMeth{}, the
%% build system forwards settings to the underlying testing framework to
%% enable parallel execution within each process in addition to running
%% test classes on different processes.

Forking OS processes to run test jobs is a common feature of build
systems as to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
Ant), this amounts to spawning one JVM instance (per process) per CPU,
on a machine with potentially many virtual CPUs, and aggregating
corresponding results when jobs finish.  Note that forking can only be
combined with configuration \SeqClassParMeth{} (see
Section~\ref{sec:frameworks}) as Maven only accepts one test class at
a time per forked process.\Mar{$\leftarrow$Are you sure about this?
  It seems silly.  Maybe, the rationale is to ``keep design simple''.}
To attenuate the non-trivial cost of spawning new processes and JVMs on
every test class, Maven offers an option to reuse the
JVM.\Mar{$\leftarrow$confirma?  se sim, pode mostrar isto na
  configuracao abaixo?}

%%We are unaware of other build system capable of running multiple
%%classes at time within a forked process.

@@

%%  LocalWords:  parallelization CPUs JUnit TestNG NUnit multi JVM de
%%  LocalWords:  JVMs falar explicar configuracao ilustrada levanta
%%  LocalWords:  uma por cria cada executar paralelo escapeinside
%%  LocalWords:  xleftmargin framexleftmargin basicstyle boxpos
%%  LocalWords:  numberstyle morekeywords threadCount forkCount
%%  LocalWords:  perCoreThreadCount reuseFork deletekeywords groupId
%%  LocalWords:  artifactId
